Coherent optical association of a single molecule -- Supplemental material

### 2020-11-24 sm.tex
Update on Overleaf.

\section{Excited Molecular States} 
To obtain a full calculation for the expected Raman Rabi frequency, light shift and scattering, we need to account for all the excited molecular states. The lowest eight molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P. These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}. We use potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ that have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}. Unfortunately, simple single-channel Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{A-b} complex \cite{Zaharova2009}. Since our experiment attempts to work in a regime where the predominant Raman coupling and scattering comes from the $v' = 0$ state of the $ \mathrm{c^3\Sigma^+_1} $, the contribution

>>>>

\section{Excited Molecular States} 
To obtain a full calculation for the expected Raman Rabi frequency, light shift and scattering, we need to account for all the excited molecular states. The lowest eight molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P. These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}. We use potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ that have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}. Unfortunately, simple single-channel potentials Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed $\mathrm{A-b}$ complex \cite{Zaharova2009}. Since our experiment attempts to work in a regime where the predominant Raman coupling and scattering comes from the $v' = 0$ state of the $ \mathrm{c^3\Sigma^+_1} $, the contribution
